Predicate Abstraction for Trace Inclusion

### 2017-07-31 symbolic_nfa_universality/symbolic_subset_construction.tex
little thing

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Emptiness and Universality of Transition Systems}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
For simplicity, let us assume that the transition system $T$ has only one visible variable $x$ and only one invisible variable $y$ (this is without loss of generality, since a variable may hold an $n$-tuple).
A trace is then just a sequence $d_0,\ldots, d_k$ of elements of the domain.
%
We will elaborate on the problems of emptiness and universality of $T$, that is, the problems of deciding whether $\lang(T) = \emptyset$ and  whether $\lang(T) = \domain^*$.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Emptiness and Universality of Transition Systems}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
For simplicity, let us assume that the transition system $T$ has only one visible variable $x$ and only one invisible variable $y$ (this is without loss of generality since $\domain$ may contain tuples).
A trace is then just a sequence $d_0,\ldots, d_k$ of elements of the domain.
%
We will elaborate on the problems of emptiness and universality of $T$, that is, the problems of deciding whether $\lang(T) = \emptyset$ and  whether $\lang(T) = \domain^*$.
